Data Management for LSST Special Programs

### 2023-10-18 sec_sci.tex
updates

\textbf{Necessary -- } When the science goals for a Special Program cannot
be met by only including the data in regular processing (e.g., Prompt processing).

@@

To further illustrate this recommendation, a few examples of Special Processing
cases are provided below.

@@

\item \textbf{Possible and necessary:}

@@

\item \textbf{Necessary but not possible:}

@@

RESTART EDITING PROCESS HERE

\textbf{Case B (possible and necessary for RDM to create separate data products) -- }
For some science goals, users will need distinct data products composed solely from visits associated with certain Special Programs (Section~\ref{ssec:proc_rdm}).
These cases are usually associated with image coaddition and the static-sky catalogs 
of sources detected and measured in the deeply coadded images.

\textbf{Case C (not possible, so user-generated data products will be needed) -- }
For some science goals, users might require unique and separate data products, 
new algorithms or processing routines, and/or significant additional 
computational resources for Special Programs.
In these situations, user processing and user-generated data products will be 
needed (Section~\ref{ssec:proc_user}).
These cases are usually related to time domain science goals that utilize 
intermediate-timescale ``custom" coadds (e.g., weekly, monthly stacks), 
science goals that require special processing like shift-and-stack techniques, 
or non-standard visits that are outside the boundaries of what the LSST
Science Pipelines can process (Section~\ref{ssec:proc_bounds}).

@@

\textbf{Special Processing should produce unique and separate data products
for Special Programs when it is both possible and necessary.}

@@

As mentioned in Section~\ref{ssec:req_ug}, Rubin Observatory will reserve 10\% of its 
total data processing capacity for users.
This component would include {\it all} user processing and re-processing of any and 
all LSST data, including Special Programs.

>>>>

\textbf{Necessary -- } When the primary science goal for a Special Program 
cannot be met by including the data in regular processing (e.g., Prompt processing),
or where doing so would compromise the WFD data products (e.g., introduce non-uniformity).

The definitions of possible and necessary are ultimately left to the
discretion of Rubin Data Management in Operations.

There are two main reasons for this recommendation.

@@

Specific examples are provided only to illustrate this recommendation,
not to place limits on what Special Processing might be done.
Note in particular that secondary science goals may be considered
to require User-Generated Processing.

@@

\item \textbf{Possible and necessary:}
in order to detect high-redshift (faint) galaxies in the DDFs,
Rubin Data Management uses the LSST Science Pipelines to deeply
coadd images for each field, and store the results of source
detection and characterization in unique and separate tables that
are included in the annual data release (Section~\ref{ssec:proc_rdm_ddf}).

@@

\item \textbf{Possible but not necessary (secondary science goals):}
a time-domain mini-survey (or DDF) has a secondary science goal of detecting
precursor outbursts for transients, which requires coadding images
within windows of days, weeks, and months to reach various depths.
This set of custom coadds may be considered as "not necessary" and requiring 
User-Generated Processing.

\item \textbf{Necessary but not possible:}
in order to find the most distant, faint Kuiper Belt Objects in the DDF,
a specialized, computationally intensive form of "shift-and-stack" processing
is required for detection, but such algorithms are not used by the 
LSST Science Pipelines and so User-Generated Processing will be needed (Section~\ref{ssec:SPCS_TNO}).
A second example here is a twilight survey that uses non-standard visits 
which are outside the boundaries of what the LSST
Science Pipelines can process (Section~\ref{ssec:proc_bounds}).

@@

@@

\textbf{All visits that \emph{can} be processed by the Prompt pipelines and generate 
alerts \emph{should} be, in support of time domain and Solar System science goals.}

The phrase ``can be processed" includes all standard and alternative visits in 
sky regions for which a template image exists.
This might also include some non-standard visits (shorter or longer exposures), 
as long as they can be processed by the Prompt pipeline and an appropriate template image exists.

Visits with very short or very long exposure times (or very bright sky 
backgrounds) might be excluded if they would need specialized algorithms for,
e.g., instrument signature removal, difference-imaging, template-generation 
(Section~\ref{ssec:proc_bounds}).

If a Special Program's primary science goal requires specialized templates and 
Prompt processing, the Data Management System will have the capability to load 
and use an alternative template for some sky regions, based on the image metadata 
(i.e., the labels described in Section~\ref{ssec:sci_labels}). 
However, there would not be enough memory to hold alternative templates 
for the whole sky.

Including visits from Special Programs in regular Prompt processing alongside
vists from the WFD program is not, in general, anticipated to affect WFD science goals.
For example, analyses for a WFD-only subset could still be done using the program and
region labels described in Section~\ref{ssec:sci_labels}.
However, a few concerns are raised in Section~\ref{ssec:proc_prompt}.

@@

Rubin Observatory will reserve 10\% of its total data processing capacity for users.
This is already a requirement, as mentioned in Section~\ref{ssec:req_ug}.

This component would include {\it all} user processing and re-processing of any and 
all LSST data, including Special Programs.
